\documentclass[week2]{csse1001}

\title{CSSE1001 Week 2 Practicals}
 
\begin{document}

\begin{frame} 
\maketitle
\end{frame}

\section{Tutor Introductions}

\begin{topic}{Blackboard}
This course uses blackboard to make announcements and to host resources which
are vital to learning the course.

\url{https://learn.uq.edu.au}

It would be good to familiarize yourself with the \texbf{Learning Resources}
section.
\end{topic}

\section{\href{https://learn.uq.edu.au}{Blackboard Demo}}

\begin{topic}{MyPyTutor}
MyPyTutor is one of the \textbf{assessment} items for this course. It consists of
programming exercises based around the content you are learning each week.

\begin{subtopic}{2-}
There are \textbf{multiple due dates} throughout the semester and you are encouraged
to skip ahead as far as you feel confident.
\end{subtopic}

\begin{subtopic}{3-}
You can access MyPyTutor through \textbf{blackboard} under the \texbf{Assessment} tab.
\end{subtopic}
\end{topic}

\section{\href{https://learn.uq.edu.au}{MyPyTutor Tour}}

\begin{topic}{Practicals Vs Tutorials}
\begin{itemize}
	\item \textbf{Practicals} are a \textbf{Q\&A} session with the tutors.
	\item \textbf{Practicals} are here to help with general queries and \textbf{assessment help}.
	\item \textbf{Tutorials} work through the \textbf{tutorial exercises}
	\item Tutors in \textbf{tutorials} will \textbf{only help with tutorial exercises}.
\end{itemize}
\end{topic}

\begin{topic}{Practicals}
With the exception of feedback sessions, practicals are not compulsory and you are welcome to attend practical sessions that you are not enrolled into.

\begin{subtopic}{2-}
\textbf{Feedback Sessions:} Practical sessions are \textbf{compulsory} in week 6 and week 10 for Tuesday-Friday practicals and week 11 for Monday practicals.
\end{subtopic}
\end{topic}

\begin{topic}{Practical Queue}
The practical queue is how we answer questions in practicals.

Following the link below and logging in with your UQ account will allow you to add yourself to the queue for a practical.

\url{https://csse1001.uqcloud.net/queue}

Students who have asked fewer questions over a 24-hour period are given higher priority so try to \textbf{refine your question before asking}.
\end{topic}

\section{\href{https://csse1001.uqcloud.net/queue}{Queue Demo}}

\begin{topic}{ECP}
The ECP of a course is the first place you should look for any of your courses at UQ.

An ECP is the official ruling on all course details i.e. assessment, policies, etc.

\url{https://my.uq.edu.au/programs-courses/course.html?course_code=CSSE1001}
\end{topic}

\section{\href{https://my.uq.edu.au/programs-courses/course.html?course_code=CSSE1001}{ECP Brief}}

\begin{topic}{Piazza}
Piazza is an \textbf{online Q\&A} platform that allows you to ask the tutor questions.

\begin{subtopic}{2-}
Piazza is useful when tutors in practicals are unavailable due to being outside of hours or practicals being very busy.
\end{subtopic}

\begin{subtopic}{3-}
Post any questions with code only to the instructors, otherwise you are highly encouraged to make your question \textbf{public} so other students can help.
\end{subtopic}

\url{https://piazza.com/class/jizcg2kjurn1kb}
\end{topic}

\end{document} 
